Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
re-worded tech perceptiosn section

\subsection{Risk and Benefit Rankings} 
When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today. The most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).

@@

Notably, technologies perceived to be beneficial include location tracking and heart rate detection. Again, we believe this is the result of exposure people have to these technologies--most people use GPS or other location-based applications on their smart phones and fitness trackers are the most popular type of wearable device. Technologies considered to be risky, such as a discrete camera and facial recognition, seemed to be based on media exposure or general aversion to privacy invasion. However, people are becoming increasingly aware of such risks and are comparing these risks of privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.

>>>>

\subsection{Risk and Benefit Rankings} 
When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today.

@@

Participants rated the the most familiar technologies as the most beneficial (top 5: internet, laptops, email, smartphones, and location tracking).  Again, we believe this is the result of exposure people have to these technologies--most people are exposed to these devices and use location-based applications. The most risky technologies were ones perceived to be privacy-invasive (bottom 5: facial recognition, internet, discreet video camera, location tracking, and facial detection). People are becoming increasingly aware of such privacy risks and are comparing these privacy invasion to real physical risks--for instance, the capacity for facial detection on a wearable device is perceived to be almost as risky as interacting with a physical lawnmower. It is fair to say that, these assessments of the most risky or beneficial technologies may not be the most accurate, but do reflect the exposure of various technologies to the general public and also prove that people do perceive risks in a real way related to these technologies.
